### 2020-07-26 draft.Rmd
removed echo, added inline R

```{r load-data}
seed011204 <-read_stata("dataverse_files/seedanalysis_011204.dta")

seed080404 <- read_stata("dataverse_files/seedanalysis_080404.dta")

combined <- read_stata("dataverse_files/seedanalysis_011204_080404.dta")

@@

```{r, }
seed_accounts = treated %>% filter(treatment == 1)
hist(seed_accounts$balchange,
     main="Histogram of balance changes for SEED accounts",
     xlab="Balance Change")

@@

The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences. The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative. The test statistic is the sum of the positive ranks. As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with $E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and $\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=299005778$. [@Higgins]

@@

```{r, echo=FALSE}
wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)

>>>>

```{r load-data}
seed011204 = read_stata("dataverse_files/seedanalysis_011204.dta")

seed080404 = read_stata("dataverse_files/seedanalysis_080404.dta")

combined = read_stata("dataverse_files/seedanalysis_011204_080404.dta")

six_months = filter(seed011204, !is.na(treatment))

@@

```{r}
seed_accounts = treated %>% filter(treatment == 1)
hist(seed_accounts$balchange,
     main="Histogram of balance changes for SEED accounts",
     xlab="Balance Change")

@@

The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences. The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative. The test statistic is the sum of the positive ranks. As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with 
$E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and 
$\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=`r (842 * (842 + 1) * (2 * 842 + 1) / 24)`$. [@Higgins]

@@

```{r}
wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
